---
title: "Popular names"
subtitle: "Week 6 Activity"
author: "Shannon Curran and Sophie Massolas"
date: "22 February 2026"
output: 
  html_notebook:
    fig_height: 3
    fig_width: 5
---

# Set Up

```{r message=FALSE}
# load necessary packages
library(tidyverse)
library(dcData)
library(mosaic)
library(esquisse)
```


```{r}
# Load the BabyNames data into RStudio environment (from dcData package)
data("BabyNames")

```

# Activity

**Goal**: By the end of the activity, each team will create a graph (like Figure A.1 on p 159) showing ups and downs in the popularity of the names at your table according to the U.S. social security registry.  


### Step 1


```{r}
## Helpful to look at the data a few different ways (see Ch 9 for more).
glimpse(BabyNames)
str(BabyNames)
summary(BabyNames)
```

### Step 2

[This should be done by hand on paper, nothing to show in the HTML doc]


### Step 3 

##### What variable(s) from the raw data table do not appear at all in the graph?

The variable "sex" would not appear in the graph.


##### What variable(s) in the graph are similar to corresponding variables in the raw data table, but might have been transformed in some way?

The variables "name," "count," and "year" will remain the same.



### Step 4

##### Have cases been filtered out?

The cases would be the most popular girl names in 1880, 1947, and 2013. The rest of the girl baby names and all boy baby names would be filtered out.


##### Have cases been grouped and summarized within groups in any way?

No, cases have not been grouped in any way.


##### Have any new variables been introduced?  If so, what the relationship between the new variables and existing variables?

No new variables have been introduced.



### Step 5



### Step 6

[This should be done by hand on paper, nothing to show in the HTML doc]



### Step 7

```{r}


```


### Graph It!

Here's the sample code provided by the book:

```
GlyphReadyForm %>%
  ggplot(aes(x = year, y = total, group = name)) + 
  geom_line(size = 1, alpha = 0.5, aes(color = name)) + 
  ylab("Popularity") + xlab("Year")
```



Note: if someone in your group has a name that hasn't been registered with the US Social Security Administration for a baby born in the United States, it's okay that the student's name may not appear on the plot.